---
title: "Classification methods"
author: "Adi Sarid / adi@sarid-ins.co.il"
date: "22 7 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
suppressMessages(library(tidyverse))
```

## Classification Methods

For some diversity, we are leaving the beer example in favour of another fun activity, watching movies.

We're going to use data which was scraped from IMDB, by sundeepblue [source](https://github.com/sundeepblue/movie_rating_prediction).

We're going to "force" the problem into a classification problem for identifying "successful movies", but from an investor's point of view, i.e., movies which earned at least 2.5 times their investment (`gross`/`budget`$\geq2.5$).

```{r read the movie db data and arrange}
movies_raw <- read_csv("https://raw.githubusercontent.com/sarid-ins/statistical_learning_course/master/datasets/scraped_imdb/movie_db_clean.csv") %>% 
  mutate(earn_ratio = gross/budget) %>% 
  mutate(success = earn_ratio >= 2.5)
```